SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-03-01 scipy-1.0/paper.tex
tightened asv section

The airspeed velocity (\texttt{asv}\cite{asvref}) library enables benchmarking Python packages
over their lifetimes, and the performance of the SciPy codebase was monitored
with \texttt{asv} starting in February of 2015 (PR \#4501). In addition to ensuring that
unit tests are passing, confirming that performance generally
remains constant or improves over the commit hash history of the project allows
us to objectively measure that our codebase is improving. Figure~\ref{fig:asvbench}
shows an example benchmark results for \texttt{scipy.spatial.cKDTree.query} over 
roughly nine years of project history.

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
\caption{Airspeed velocity benchmarks for \texttt{scipy.spatial.cKDTree.query}. 
The results are based on
Python 2.7 performance on the master branch of the project using NumPy 1.8.2
and Cython versions 0.27.3, 0.21.1, and 0.18 (for improved backward
compatibility). Only the L2 (Euclidean) norm is shown here, and to improve
backward compatibility and sampling of the benchmarks there was no application
of toroidal topology to the \texttt{KDTree} (\texttt{boxsize} argument was ignored). Such results
can be generated using can be run using the command:
\texttt{python run.py run -e -s 800 --bench "\textbackslash
btime\_query\textbackslash b" "02de46a546..b3ddb2c"},
where \texttt{run.py} is a light wrapper script around \texttt{asv}
that is packaged with SciPy.}
\label{fig:asvbench}
\end{figure}

Any pull request can be compared against the \texttt{master} branch with the
command \texttt{asv continuous master new-feature}. This will provide a
benchmark against the master branch and the branch a new feature is implemented
in. More features are available in the \texttt{asv} documentation\cite{asvdocs}, including 
arguments to select which benchmarks to run.

>>>>

In addition to ensuring that unit tests are passing, it is important to ensure that the
the performance of the SciPy codebase improves over time. Since February 2015, the 
performance of the SciPy codebase has been monitored with Airspeed Velocity
(\texttt{asv}\cite{asvref}) library. Figure~\ref{fig:asvbench}
shows example benchmark results for \texttt{scipy.spatial.cKDTree.query} over 
roughly nine years of project history.

\begin{figure}[H]
\centering
\includegraphics[width=\textwidth]{static/asv_time_query_ckdtree}
\caption{Airspeed velocity benchmarks for \texttt{scipy.spatial.cKDTree.query}. 
The results are based on
Python 2.7 performance on the master branch of the project using NumPy 1.8.2
and Cython versions 0.27.3, 0.21.1, and 0.18 (for improved backward
compatibility). Only the L2 (Euclidean) norm is shown here, and to improve
backward compatibility and sampling of the benchmarks there was no application
of toroidal topology to the \texttt{KDTree} (i.e. the \texttt{boxsize} argument 
was ignored).}
\label{fig:asvbench}
\end{figure}
